Brundle Development

### 2018-02-20 Manuscript_Figures.Rmd
Corrected headings

>>>>

```{r,results='hide', message=FALSE, warning=FALSE}

jg.experimentPeaksetNormalised<-Brundle(
            dbaExperiment,
            dbaControl,
            jg.treatedCondition,
            jg.untreatedCondition,
            jg.experimentSampleSheet,
            jg.controlSampleSheet )

```{r,results='hide', message=FALSE, warning=FALSE}

##PDX Analysis

```{r, results='hide', message=FALSE, warning=FALSE}

pdx<-readRDS(file="Rdata/pdx.rds")
ctcf<-readRDS(file="Rdata/ctcf.rds")

pdx<- dba.count(pdx,peaks = NULL, score = DBA_SCORE_READS)
ctcf<- dba.count(ctcf,peaks = NULL, score = DBA_SCORE_READS)

peakset.ctcf <- dba.peakset(ctcf, bRetrieve = TRUE, DataType = DBA_DATA_FRAME)
peakset.er <- dba.peakset(pdx, bRetrieve = TRUE, DataType = DBA_DATA_FRAME)

normalisation.factor<-colSums(peakset.ctcf[4:8])/median(colSums(peakset.ctcf[4:8]))

normalised.er<-cbind(peakset.er[1:3],peakset.er[4]/normalisation.factor[1],
                                     peakset.er[5]/normalisation.factor[2],
                                     peakset.er[6]/normalisation.factor[3],
                                     peakset.er[7]/normalisation.factor[4],
                                     peakset.er[8]/normalisation.factor[5])

colSums(normalised.er[4:8])
colSums(peakset.er[4:8])

normalised.ctcf<-cbind(peakset.ctcf[1:3],
                       peakset.ctcf[4]/normalisation.factor[1],
                       peakset.ctcf[5]/normalisation.factor[2],
                       peakset.ctcf[6]/normalisation.factor[3],
                       peakset.ctcf[7]/normalisation.factor[4],
                       peakset.ctcf[8]/normalisation.factor[5])

colSums(normalised.ctcf[4:8])

rpm<-as.numeric(pdx$class["Reads",])/10^6

addToDf<-function(data,factor,method,locus) {
        data.frame(counts=as.numeric(t(data)),factor=rep(factor,4),method=rep(method,4),rep=c("PDX01","PDX03","PDX04","PDX05"),locus=rep(locus,4))
}

library(ggpubr)

relativeRPM<-(rpm[c(1,3:5)]/median(rpm[c(1,3:5)]))

df<-addToDf(peakset.ctcf[13416,c(4,6:8)],"CTCF","Raw","RARa")
df<-rbind(df,addToDf(peakset.er[639,c(4,6:8)],"ER","Raw","RARa"))
df<-rbind(df,addToDf(peakset.ctcf[13416,c(4,6:8)]/relativeRPM,"CTCF","RPM","RARa"))
df<-rbind(df,addToDf(peakset.er[639,c(4,6:8)]/relativeRPM,"ER","RPM","RARa"))
df<-rbind(df,addToDf(normalised.ctcf[13416,c(4,6:8)],"CTCF","pfChIP","RARa"))
df<-rbind(df,addToDf(normalised.er[639,c(4,6:8)],"ER","pfChIP","RARa"))

ctcfSite<-"21382"
erSite<-"891"
name<-"GREB1"
df<-rbind(df,addToDf(peakset.ctcf[ctcfSite,c(4,6:8)],"CTCF","Raw",name))
df<-rbind(df,addToDf(peakset.er[erSite,c(4,6:8)],"ER","Raw",name))
df<-rbind(df,addToDf(normalised.ctcf[ctcfSite,c(4,6:8)],"CTCF","pfChIP",name))
df<-rbind(df,addToDf(normalised.er[erSite,c(4,6:8)],"ER","pfChIP",name))
df<-rbind(df,addToDf(peakset.ctcf[ctcfSite,c(4,6:8)]/relativeRPM,"CTCF","RPM",name))
df<-rbind(df,addToDf(peakset.er[erSite,c(4,6:8)]/relativeRPM,"ER","RPM",name))

ctcfSite<-"20453"
erSite<-"1064"
name<-"CLIC6"
df<-rbind(df,addToDf(peakset.ctcf[ctcfSite,c(4,6:8)],"CTCF","Raw",name))
df<-rbind(df,addToDf(peakset.er[erSite,c(4,6:8)],"ER","Raw",name))
df<-rbind(df,addToDf(normalised.ctcf[ctcfSite,c(4,6:8)],"CTCF","pfChIP",name))
df<-rbind(df,addToDf(normalised.er[erSite,c(4,6:8)],"ER","pfChIP",name))
df<-rbind(df,addToDf(peakset.ctcf[ctcfSite,c(4,6:8)]/relativeRPM,"CTCF","RPM",name))
df<-rbind(df,addToDf(peakset.er[erSite,c(4,6:8)]/relativeRPM,"ER","RPM",name))

ggbarplot(df, x="rep", y = "counts",
          fill = "method",    
          color = "white",            # Set bar border colors to white
          palette =c("#FC4E07", "#E7B800", "#00AFBB"),
          sort.by.groups = FALSE,     # Don't sort inside each group
          x.text.angle = 90,          # Rotate vertically x axis texts
          ylab = "Corrected Counts",
          xlab = "PDX",
          legend.title = "Comparison",
          facet.by=c("locus","factor"),
          position=position_dodge(width=0.7)
)

ggboxplot(df, x="method", y = "counts",
          palette =c("#FC4E07", "#E7B800", "#00AFBB"),
          ylab = "Corrected Counts",
          xlab = "PDX",
          color="method",
          facet.by=c("locus","factor"),
          legend.title = "Comparison"
)

```{r, results='hide', message=FALSE, warning=FALSE}
#Homer profile

ctcf<-read.table("SLX-15439/blacklist_filtered/Homer_CTCF_Profile.txt", sep="\t", header=TRUE)
er<-read.table("SLX-15439/blacklist_filtered/Homer_ER_Profile.txt", sep="\t", header=TRUE)

par(mfrow=c(2,2))
profile_CTCF<-as.matrix(ctcf[,c(1,2,5,8,11)])
plot(profile_CTCF,t="l",lwd=3,col="#00AFBB", xlab="Distance from Summit",ylab="Read Depth",main="CTCF Profile")
lines(profile_CTCF[,c(1,3)],lwd=3,col="#E7B800")
lines(profile_CTCF[,c(1,4)],lwd=3,col="#FC4E07")
lines(profile_CTCF[,c(1,5)],lwd=3,col="#FC00FE")
legend("topright",legend = c("PDX01", "PDX03", "PDX04", "PDX05"), col=c("#00AFBB","#E7B800", "#FC4E07","#FC00FE"),pch = c(19,19))

maxCTCF<-colMaxs(profile_CTCF)
minCTCF<-colMins(profile_CTCF)

profile_CTCF[,2:5]<-profile_CTCF[,2:5]-minCTCF[2:5]

colSums(profile_CTCF[,2:5]/maxCTCF[2:5])
normalised_CTCF<-t((t(profile_CTCF[,2:5])/maxCTCF[2:5]))
normalised_CTCF<-cbind(profile_CTCF[,1],normalised_CTCF)

plot(normalised_CTCF,lwd=3,t="l",col="#00AFBB", xlab="Distance from Summit",ylab="Read Depth",main="Normalised CTCF Profile")
lines(normalised_CTCF[,c(1,3)],lwd=3,col="#E7B800")
lines(normalised_CTCF[,c(1,4)],lwd=3,col="#FC4E07")
lines(normalised_CTCF[,c(1,5)],lwd=3,col="#FC00FE")
legend("topright",legend = c("PDX01", "PDX03", "PDX04", "PDX05"), col=c("#00AFBB","#E7B800", "#FC4E07","#FC00FE"),pch = c(19,19))

profile_ER<-as.matrix(er[,c(1,2,5,8,11)])
plot(profile_ER,t="l",lwd=3,col="#00AFBB", xlab="Distance from Summit",ylab="Read Depth",main="ER Profile")
lines(profile_ER[,c(1,3)],lwd=3,col="#E7B800")
lines(profile_ER[,c(1,4)],lwd=3,col="#FC4E07")
lines(profile_ER[,c(1,5)],lwd=3,col="#FC00FE")
legend("topright",legend = c("PDX01", "PDX03", "PDX04", "PDX05"), col=c("#00AFBB","#E7B800", "#FC4E07","#FC00FE"),pch = c(19,19))

normalised_ER<-t((t(profile_ER[,2:5])/maxCTCF[2:5]))
normalised_ER<-cbind(profile_ER[,1],normalised_ER)

plot(normalised_ER,t="l",lwd=3,col="#00AFBB", xlab="Distance from Summit",ylab="Read Depth",main="Normalised ER Profile")
lines(normalised_ER[,c(1,3)],lwd=3,col="#E7B800")
lines(normalised_ER[,c(1,4)],lwd=3,col="#FC4E07")
lines(normalised_ER[,c(1,5)],lwd=3,col="#FC00FE")
legend("topright",legend = c("PDX01", "PDX03", "PDX04", "PDX05"), col=c("#00AFBB","#E7B800", "#FC4E07","#FC00FE"),pch = c(19,19))
